\vspace{-2cm} Government Websites As Data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2021-06-04 paper/jitp_cover_letter/jitp_cover_letter_rr.tex
resubmitted files

\opening{Dear JITP Editorial Team:}
\medskip

% overview of Ted
%% He took my course, has worked as my RA, is my advisee, has R&R at PSRM

We are very excited for the opportunity to have our manuscript entitled, ``Government Websites As Data:  A methodological pipeline with application to the websites of municipalities in the United States,'' considered for publication at {\em The Journal of Information Technology \& Politics}.  We introduce a novel methodological pipeline, along with statistical software that we have developed, for automatically scraping and processing substantive text from large sets of government websites. Our contribution lies in the fact that our methodology is capable of cutting through heterogeneous file types and site organizations to extract substantively meaningful and representative blocks of plain text. We illustrate this methodology with an application to a large sample of the websites of U.S. municipal governments, and find that the textual content of websites varies systematically with the partisanship of the mayor.

We have presented our work in the form of a Workbench Note. As JITP readers and contributors are likely to engage with research problems that involve the collection of website contents, we see JITP as an ideal outlet in which to publish our research. We appreciate your consideration of our work, and welcome feedback on our manuscript.

>>>>

\opening{Dear {\em JITP} Editorial Team:}
\medskip

We greatly appreciate the opportunity to revise and resubmit our manuscript entitled, ``Government Websites As Data:  A methodological pipeline with application to the websites of municipalities in the United States,'' for publication at {\em The Journal of Information Technology \& Politics}.  Revising in response to the reviewer comments has sharpened the communication of our contributions, and improved the paper overall.  We are excited to continue developing our manuscript with the guidance of the {\em JITP} editorial team and reviewers.

### 2021-06-04 paper/manuscript_jitp_rr-attributed.tex
resubmitted files

%\author{ Markus Neumann\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA. Email: mvn5218@psu.edu. Corresponding author.} \and Fridolin Linder\footnote{Department of Political Science, Social Media and Political Participation Lab, New York University, New York, NY 10012, USA. Email: fridolin.linder@nyu.edu} \and Bruce Desmarais\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA. Email: bdesmarais@psu.edu. This work was supported by the National Science Foundation [1320219, 1637089, 1641047].}} \date{\today}

>>>>

\author{ Markus Neumann\footnote{Wesleyan Media Project, Postdoctoral Research Fellow,  Wesleyan University, Middletown, CT 06459, USA. Email: mneumann01@wesleyan.edu. Corresponding author.} \and Fridolin Linder\footnote{Department of Political Science, Social Media and Political Participation Lab, New York University, New York, NY 10012, USA. Email: fridolin.linder@nyu.edu} \and Bruce Desmarais\footnote{Department of Political Science, The Pennsylvania State University, University Park, PA 16802, USA. Email: bdesmarais@psu.edu. This work was supported by the National Science Foundation [1320219, 1637089, 1641047].}} \date{\today}
